Near infrared spectrum of a Class 0 protostar photosphere

### 2017-05-15 document/ms.tex
Now also posting the ms.tex content to sharelatex

\section{Introduction}\label{sec:intro}
The method is from \citep{czekala16}.  It is similar to \citep{2017ApJ...836..200G}.

@@

Our approach involves Bayesian forward modeling of the observed spectrum under a range of different assumptions about the prostellar system.  We discuss the limitations of our assumptions in the discussion section.

@@

We assume that stellar photosphere and warm circumstellar disk emission dominate the radiation in the near-IR band.  We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala16} with support for mixture model modifications from \citet{2017ApJ...836..200G}.  The mixture model for S68N's Keck spectrum is:

@@

$$ A_\lambda / A_K = \frac{\lambda}{2.2 \; \mu\mathrm{m}}^\alpha$$

with $\alpha \in [-2, -1.7]$ representing the power law exponent that may depend on dust properties and degree of extinction.

>>>>

\section{Introduction}\label{sec:intro}
The method is from \citep{czekala15}.  It is similar to \citep{2017ApJ...836..200G}.

@@

Our approach involves Bayesian forward modeling of the observed spectrum under a range of different assumptions about the protostellar system.  We discuss the limitations of our assumptions in the discussion section.

@@

We assume that stellar photosphere and warm circumstellar disk emission dominate the radiation in the near-IR $K-$band.  We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala15} with support for mixture model modifications from \citet{2017ApJ...836..200G}.  The mixture model for S68N's Keck spectrum is:

@@

$$ A_\lambda / A_K = \frac{\lambda}{2.2 \; \mu\mathrm{m}}^{-\alpha}$$

with $\alpha \in [-2, -1.7]$ representing the power law exponent that may depend on dust properties and degree of extinction.  The extinction is then defined as:

$$ 10^{-0.4 A_\lambda}$$
